Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-04 main.tex
Tidy up captions.
Also remove count from tables and automatically generate these from nb.

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_scores_summary.tex}
        \caption{Standard Tournament: Top Ranking Strategies by median score
        (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:standard_score}
\end{table}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
        \caption{Ranking by median score for the Standard Tournament}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
    \caption{Pairwise Match results for the Standard Tournament}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_wins_boxplots.pdf}
        \caption{Ranking by Total wins for the Standard Tournament}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_wins_summary.tex}
        \caption{Standard Tournament: Number of wins of Top Ranking Strategies
        by median score (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:standard_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_ranks_summary.tex}
        \caption{Standard Tournament: Ranks of Top Ranking Strategies
        by median score (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_ranks_boxplots.pdf}
        \caption{Rankings over each repeated tournament}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_scores_summary.tex}
        \caption{Noisy Tournament: Top Ranking Strategies by Median Score in a
        15000 Tournaments with 5\% noise}
        \label{tbl:noisy_score}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
        \caption{Ranking by Median Payoff for the Noisy Tournament}
        \label{fig:noisy_score}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
    \caption{Pairwise Match results for the Noisy Tournament}
    \label{fig:noisy_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/noisy_wins_boxplots.pdf}
        \caption{Ranking by Total wins for the Noisy Tournament}
        \label{fig:noisy_winplot}
    \end{figure}
\end{landscape}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_wins_summary.tex}
        \caption{Noisy Tournament: Number of wins of Top Ranking Strategies
        by median score (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:noisy_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_ranks_summary.tex}
        \caption{Noisy Tournament: Ranks of Top Ranking Strategies
        by median score (50th percentile) in 15,000 Tournaments}
        % TODO Update caption as more repetitions are carried out
        % TODO Potentially remove count from table (including it for now so as
        % to avoid confusion.
        \label{tbl:noisy_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/noisy_ranks_boxplots.pdf}
        \caption{Rankings over each repeated tournament}
        \label{fig:noisy_ranks_boxplot}
    \end{figure}
\end{landscape}

>>>>

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_scores_summary.tex}
        \caption{Standard Tournament: Mean score per turn of top 15 strategies
            (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:standard_score}
\end{table}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{./assets/standard_scores_boxplots.pdf}
        \caption{Standard Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{fig:standard_boxplot}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \includegraphics[width=\textwidth]{./assets/standard_scores_heatmap.pdf}
    \caption{Standard Tournament: Mean score per turn of row players against
    column players (ordered by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
    \label{fig:standard_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_wins_boxplots.pdf}
        \caption{Standard Tournament: number of wins per tournament (ordered by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{fig:standard_winplot}
    \end{figure}
\end{landscape}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_wins_summary.tex}
        \caption{Standard Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:standard_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/standard_top_15_ranks_summary.tex}
        \caption{Standard Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{tbl:standard_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/standard_ranks_boxplots.pdf}
        \caption{Standard Tournament: rank in each tournament (ordered by
        median over
        \protect\input{./assets/standard_number_of_repetitions.tex}tournaments)}
        \label{fig:standard_ranks_boxplot}
    \end{figure}
\end{landscape}

@@

% Table of best strategies
\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_scores_summary.tex}
        \caption{Noisy (5\%) Tournament: Mean score per turn of top 15 strategies
        (ranked by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{tbl:noisy_score}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \includegraphics[width=\paperwidth]{./assets/noisy_scores_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: Mean score per turn (ranked by median
        over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{fig:noisy_score}
    \end{figure}
\end{landscape}

@@

\begin{figure}[!hbtp]
    \includegraphics[width=\textwidth]{./assets/noisy_scores_heatmap.pdf}
    \caption{Noisy (5\%) Tournament: Mean score per turn of row players against
    column players (ordered by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
    \label{fig:noisy_heatmap}
\end{figure}

@@

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/noisy_wins_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: number of wins per tournament (ordered by
        median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{fig:noisy_winplot}
    \end{figure}
\end{landscape}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_wins_summary.tex}
        \caption{Noisy (5\%) Tournament: Number of wins per tournament
        of top 15 strategies (ranked by median score over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{tbl:noisy_wins}
\end{table}

@@

\begin{table}[!hbtp]
    \centering
        \input{./assets/noisy_top_15_ranks_summary.tex}
        \caption{Noisy (5\%) Tournament: Rank in each tournament
        of top 15 strategies (ranked by median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{tbl:noisy_ranks}
\end{table}

\begin{landscape}
    \begin{figure}[!hbtp]
        \centering
        \includegraphics[width=\textwidth]{./assets/noisy_ranks_boxplots.pdf}
        \caption{Noisy (5\%) Tournament: rank in each tournament (ordered by
        median over
        \protect\input{./assets/noisy_number_of_repetitions.tex}tournaments)}
        \label{fig:noisy_ranks_boxplot}
    \end{figure}
\end{landscape}
